---
title: "hw6_yl4608"
author: "Yutian Luo"
date: "12/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(p8105.datasets)
library(broom)
library(sjPlot)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() +  theme(legend.position = "bottom"))

options(
  ggplots2.continuous.color = "viridis",
  ggplots2.continuous.fill = "viridus"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



# ` Problem 1` 

The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here. You can read their accompanying article here.

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r import clean}

homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1,
    )) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)

```


For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

```{r glm logistic }

baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm( 
  resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
      family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate), #odds ratio
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)

```


Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing Black victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.


```{r glm accross country}

models_results_df =
homicide_df %>% 
  nest(data = -city_state) %>% # data is everything except for cities
  mutate(
    models = map(.x = data, ~ glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% #pull(results)
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate), #odds ratio
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))

```


Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r glm res plot}

models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state,OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```


# `Problem 2`


In this problem, you will analyze data gathered to understand the effects of several variables on a child’s birthweight. This dataset, available here, consists of roughly 4000 children and includes the following variables:

```{r import birth}

birthw_data = 
  read.csv("./data/birthweight.csv")

```


babysex: baby’s sex (male = 1, female = 2)
bhead: baby’s head circumference at birth (centimeters)
blength: baby’s length at birth (centimeteres)
bwt: baby’s birth weight (grams)
delwt: mother’s weight at delivery (pounds)
fincome: family monthly income (in hundreds, rounded)
frace: father’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other, 9 = Unknown)
gaweeks: gestational age in weeks
malform: presence of malformations that could affect weight (0 = absent, 1 = present)
menarche: mother’s age at menarche (years)
mheigth: mother’s height (inches)
momage: mother’s age at delivery (years)
mrace: mother’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other)
parity: number of live births prior to this pregnancy
pnumlbw: previous number of low birth weight babies
pnumgsa: number of prior small for gestational age babies
ppbmi: mother’s pre-pregnancy BMI
ppwt: mother’s pre-pregnancy weight (pounds)
smoken: average number of cigarettes smoked per day during pregnancy
wtgain: mother’s weight gain during pregnancy (pounds)


## 1. Load and clean the data for regression analysis 
(i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r load clean}

birthw_data = 
  birthw_data %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>% 
  relocate(bwt)

```


## 2. Propose a regression model for birthweight. 

This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r model birthwt}

# Multi var all predictors
fit_all = lm(bwt~., birthw_data)
summary(fit_all)

# aic procedure
aic_res = step(fit_all, direction = "backward")
summary(aic_res)

# drop variables
aic_res2 = update(aic_res, .~. -fincome)
summary(aic_res2)

```

First, I performed regression and conducted feature selection based on AIC stepwise regression.

The result was then further examined and I dropped 'fincome' predictor since its insignificant.

Last, the fitted model is $$\hat{bwt} = 28.3735\times\hat{babysex}+131.0228\times\hat{bhead}+74.7933\times\hat{blength}+4.0840\times\hat{delwt}+11.6785\times\hat{gaweeks}+6.8569\times\hat{mheight}-145.3753\times\hat{mrace2}-77.9781\times\hat{mrace3}-105\times\hat{mrace4}+94\times\hat{parity}-2\times\hat{ppwt}-4\times\hat{smoken}$$


```{r diagnostics}

brithw_data %>% 
  modelr::add_residuals(aic_res2) %>% 
  modelr::add_predictions(aic_res2) %>% 
  ggplot(aes(pred, resid))+
  geom_point()+
  geom_smooth(method = "loess")+
  xlab("Predict/Fit")+
  ylab("Residual")+
  ggtitle("Residual Fitted plot")

```



Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r compare models}

mod_f1 = lm(bwt ~ blength + gaweeks, birthw_data)
tidy(mod_f1)

mod_f2 = lm(bwt ~ babysex*bhead*blength, birthw_data)
tidy(mod_f2)


# show models
mlr_tab =
  tab_model(mod_f1,mod_f2,aic_res2)

```


Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r cv}

cv_df = 
  crossv_mc(birthw_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

# cross validation

cv_df = 
  cv_df %>% 
  mutate(
    aic_res2 = map(.x = train, ~lm(formula = bwt ~ babysex + bhead + blength + delwt + gaweeks + 
    mheight + mrace + parity + ppwt + smoken, data = .x)),
    mod_f1 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_f2 = map(.x = train, ~lm(bwt ~ babysex*bhead*blength, data = .x))
  )%>% 
  
  mutate(
     rmse_aic2 = map2_dbl(.x = aic_res2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_f1 = map2_dbl(.x = mod_f1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_f2 = map2_dbl(.x = mod_f2, .y = test, ~rmse(model = .x, data = .y))
  )

# mean prediction error








```


# `problem 3`
















